---
title: "iNaturalist_Harmonia_Hesperomyces_Quebec"
author: "Jonathan Cazabonne"
date: "2025-03-17"
output:
  html_document:
    df_print: paged
---
```{r}
citation("sf") #check current R version and citations for used packages
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# iNaturalist_harmonia_laboul_QC

## Perfomed under R 2024.12.1+563

## R script partly adapted from Riquelme (2024, preprint) 
- Cristian Riquelme. (2024). iNaturalist as a platform for documenting Chilean funga. EcoEvoRxiv. <https://doi.org/10.32942/X25G9D>

## Geospatial analysis are based on the following documentation:
- <https://pmarchand1.github.io/atelier_rgeo/rgeo_workshop.html>
- <https://bookdown.org/brianwood1/QDASS/simple-static-maps.html>
- <https://www.donneesquebec.ca/recherche/dataset/decoupages-administratifs> 

------------------------------------------------------------------------

# R script

## Work space preparation

### Set working directory

```{r}
setwd("/Users/jonathancazabonne/Documents/Article/iNaturalist Quebec analysis/Harmonia QC")
```

### Loading packages

```{r}
library(tidyverse)
library(sf)
library(dplyr)
```

### Establish personalized theme for the figures made using ggplot2

```{r}
mytheme <- theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

### Import dataset with iNaturalist observations of Harmonia axyridis in Quebec (extracted on the 28th February 2025)

```{r}
inat_harmonia <- "./Harmonia_laboul_checked_20250317.csv"
```

### Making sure columns we are using for further analysis are in the right format

```{r}
Harmonia <- read.csv(inat_harmonia) %>% mutate_at(c("Infection_status", "Age", "Month", "Year", "quality_grade"), as.factor) %>% mutate_at("observed_on", as.Date)
```

### Subsetting only observations of adults ladybirds, larva and pupa, and research grade observations

```{r}
Harmonia_adult <- Harmonia %>% filter(Age == "Adult")
Harmonia_adult_research_grade <- Harmonia_adult %>% filter(quality_grade == "research")
Harmonia_larva_pupa <- Harmonia %>% filter(Age %in% c("Juvenile", "In transition"))
Harmonia_research_grade <- Harmonia %>% filter(quality_grade == "research")

write.csv(Harmonia_adult, "Harmonia_adult_QC_20250317.csv", row.names = FALSE)
write.csv(Harmonia_adult_research_grade, "Harmonia_adult_research_grade_QC_20250317.csv", row.names = FALSE)
write.csv(Harmonia_larva_pupa, "Harmonia_larva_pupa_QC_20250317.csv", row.names = FALSE)
write.csv(Harmonia_research_grade, "Harmonia_research_grade_QC_20250317.csv", row.names = FALSE)
```

## Data exploration
### Histograms for quality grade

```{r}
Harmonia_quality_grade_counts <- Harmonia %>%
  group_by(quality_grade) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(Harmonia_quality_grade_counts)
```

```{r}
Harmonia$quality_grade <- factor(Harmonia$quality_grade, levels = Harmonia_quality_grade_counts$quality_grade)

cb_palette_age <- c("#D55E00", "#56B4E9", "#009E73", "#F0E442")

Harmonia %>%
  ggplot(aes(x = quality_grade, fill = Age, colour = Age)) + 
  geom_bar(alpha = 0.8) +
  mytheme +
  scale_fill_manual(values = cb_palette_age) + 
  scale_colour_manual(values = cb_palette_age) -> Harmonia_quality_grade
print(Harmonia_quality_grade)
```

```{r}
ggsave(filename = "Harmonia_quality_grade.png", plot = Harmonia_quality_grade, width = 6, height = 4, dpi = 1000)
```

### Histograms for age categories (Adults, larva, pupa)

```{r}
Harmonia_age_counts <- Harmonia %>% ## pour l'ensemble des observations
  group_by(Age) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(Harmonia_age_counts)
```

```{r}
Harmonia$Age <- factor(Harmonia$Age, levels = Harmonia_age_counts$Age)

cb_palette_quality <- c("#0072B2", "#E69F00", "#CC79A7")

Harmonia %>% 
  mutate(Age = as.factor(Age)) %>%
  ggplot(aes(x = Age, fill = quality_grade, colour = quality_grade)) + 
  geom_bar(alpha = 0.8) + 
  labs(x = "Age categories", y = "Number of observations") + 
  guides(colour = FALSE) + 
  mytheme + 
  theme(legend.title = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_manual(values = cb_palette_quality) + 
  scale_colour_manual(values = cb_palette_quality) +
   theme(aspect.ratio = 0.8) -> Age_plot
```

```{r}
Age_plot
```

/FIGURE 1A
```{r}
ggsave(filename = "Age_plot_FINAL.pdf", plot = Age_plot, width = 6, height = 4, dpi = 1000)
```

```{r}
Harmonia_research_grade_age_counts <- Harmonia_research_grade %>%
  group_by(Age) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(Harmonia_research_grade_age_counts)
```

```{r}
Harmonia_research_grade$Age <- factor(Harmonia_research_grade$Age, levels = Harmonia_research_grade_age_counts$Age)

cb_palette_age <- c("#D55E00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#E69F00", "#CC79A7")

Harmonia_research_grade %>% 
  mutate(Age = as.factor(Age)) %>%
  ggplot(aes(x = Age, fill = Age, colour = Age)) + 
  geom_bar(alpha = 0.8) + 
  labs(x = "Age categories", y = "Number of observations") + 
  guides(colour = "none") + 
  mytheme + 
  theme(legend.title = element_text(size = 12), 
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_manual(values = cb_palette_age) + 
  scale_colour_manual(values = cb_palette_age) -> Age_research_grade_plot
```

```{r}
Age_research_grade_plot
```


### Histograms for infection status (Yes, no, suspected)

```{r}
Infection_counts <- Harmonia_adult_research_grade %>%
  group_by(Infection_status) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(Infection_counts)
```

```{r}
Harmonia_adult_research_grade$Infection_status <- factor(Harmonia_adult_research_grade$Infection_status, levels = Infection_counts$Infection_status)

cb_palette_infection <- c("#E69F00", "#56B4E9", "#009E73")

Harmonia_adult_research_grade %>% 
  mutate(Infection_status = as.factor(Infection_status)) %>%
  ggplot(aes(x = Infection_status, fill = Infection_status)) + 
  geom_bar(alpha = 0.8) + 
  labs(x = "Visible infection status", y = "Number of observations") + 
  mytheme + 
  theme(legend.title = element_text(size = 12), 
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = cb_palette_infection) + 
  scale_colour_manual(values = cb_palette_infection) +
   theme(aspect.ratio = 0.8) -> Infection_plot
```

```{r}
Infection_plot
```

/FIGURE 1B
```{r}
ggsave(filename = "Infection_plot_FINAL.pdf", plot = Infection_plot, width = 6, height = 4, dpi = 1000)
```

### Histograms for month and years

```{r}
month_counts <- Harmonia_research_grade %>%
  group_by(Month) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(month_counts)
```

```{r}
year_counts <- Harmonia_research_grade %>%
  group_by(Year) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(year_counts)
```


```{r}
Harmonia_research_grade$Month <- factor(Harmonia_research_grade$Month, levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

library(RColorBrewer)
cb_palette_month <- brewer.pal(12, "Set3")

Harmonia_research_grade %>% 
  filter(!is.na(observed_on)) %>%
  mutate(Month = as.factor(Month)) %>%
  ggplot(aes(x = Month, fill = Age)) + 
  geom_bar(alpha = 0.8) + 
  scale_y_continuous(limits = c(0, 1400), expand = c(0, 0)) +
  mytheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = cb_palette_age) +
  theme(aspect.ratio = 0.8) -> month_plot
```

```{r}
month_plot
```
/FIGURE 2B
```{r}
ggsave(filename = "month_plot_FINAL.pdf", plot = month_plot, width = 6, height = 9, dpi = 1000)
```

```{r}
Harmonia_research_grade$Year <- factor(Harmonia_research_grade$Year, levels = sort(unique(Harmonia_research_grade$Year)))

library(RColorBrewer)
cb_palette_year <- brewer.pal(12, "Set2")

Harmonia_research_grade %>% 
  filter(!is.na(observed_on)) %>%
  mutate(Year = as.factor(Year)) %>%
  ggplot(aes(x = Year, fill = Age)) + 
  geom_bar(alpha = 0.8) + 
  mytheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = cb_palette_age) +
   theme(aspect.ratio = 0.8) -> year_plot
```

```{r}
year_plot
```

/FIGURE 2A
```{r}
ggsave(filename = "year_plot_FINAL.pdf", plot = year_plot, width = 6, height = 4, dpi = 1000)
```

## Accumulation of observations through time

```{r}
Harmonia_research_grade_time_cleaned <- Harmonia_research_grade %>% filter(!is.na(observed_on))

Cumulative_data_harmonia <- Harmonia_research_grade_time_cleaned %>%
  group_by(observed_on, Age) %>%
  summarise(count = n()) %>%
  arrange(observed_on) %>%
  group_by(Age) %>%
  mutate(cum_sum = cumsum(count)) %>%
ungroup() %>%
  complete(observed_on = seq.Date(min(observed_on), max(observed_on), by = "day"), Age, fill = list(count = 0, cum_sum = 0)) %>%
  group_by(Age) %>%
  mutate(cum_sum = cumsum(count))
  
Harmonia_accumulation_plot <- Cumulative_data_harmonia %>%
  ggplot(aes(x = observed_on, y = cum_sum, fill = Age)) + 
  geom_area(alpha = .8) + 
  scale_x_date(limits = as.Date(c("1995-07-18", "2025-02-22"))) + 
  labs(title = "Accumulation curve of infection observations in Quebec", 
       x = "Time", 
       y = "Number of observations") + 
  mytheme + 
  scale_fill_manual(values = cb_palette_age) +  theme(aspect.ratio = 0.8)
```

```{r}
Harmonia_accumulation_plot
```
/FIGURE 2C
```{r}
ggsave(filename = "Harmonia_accumulation_plot_FINAL.pdf", plot = Harmonia_accumulation_plot, width = 6, height = 4, dpi = 1000)
```


## Accumulation of infection observations through time

```{r}
Harmonia_adult_research_grade_time_cleaned <- Harmonia_adult_research_grade %>% filter(!is.na(observed_on))

Cumulative_data_infection <- Harmonia_adult_research_grade_time_cleaned %>%
  group_by(observed_on, Infection_status) %>%
  summarise(count = n()) %>%
  arrange(observed_on) %>%
  group_by(Infection_status) %>%
  mutate(cum_sum = cumsum(count)) %>%
ungroup() %>%
  complete(observed_on = seq.Date(min(observed_on), max(observed_on), by = "day"), Infection_status, fill = list(count = 0, cum_sum = 0)) %>%
  group_by(Infection_status) %>%
  mutate(cum_sum = cumsum(count))
  
Infection_accumulation_plot <- Cumulative_data_infection %>%
  ggplot(aes(x = observed_on, y = cum_sum, fill = Infection_status)) + 
  geom_area(alpha = .8) + 
  scale_x_date(limits = as.Date(c("1995-07-18", "2025-02-22"))) + 
  labs(title = "Accumulation curve of infection observations in Quebec", 
       x = "Time", 
       y = "Number of observations") + 
  mytheme + 
  scale_fill_manual(values = cb_palette_infection) + theme(aspect.ratio = 0.8)
```

```{r}
Infection_accumulation_plot
```

/FIGURE 2D
```{r}
ggsave(filename = "Infection_accumulation_plot_FINAL.pdf", plot = Infection_accumulation_plot, width = 6, height = 4, dpi = 1000)
```

## Map of observations of Harmonia axyridis across Quebec

```{r}
library(sf)
mrc <- st_read("SHP/mrc_l.shp")
```

```{r}
mrc_qc <- st_read("SHP/mrc_s.shp")
head(mrc_qc)
```

```{r}
# Filter the data for infected observations
infected_data <- Harmonia_adult_research_grade %>% filter(Infection_status == "Yes")

# Convert the infected data to an sf object
infected_data_sf <- st_as_sf(infected_data, coords = c("longitude", "latitude"), crs = 4326)

Harmonia_adult_research_grade_sf <- st_as_sf(Harmonia_adult_research_grade, coords = c("longitude", "latitude"), crs = 4326)

host_parasite_data_sf <- sf::st_as_sf(host_parasite_data, coords = c("longitude", "latitude"), crs = 4326)

plot(infected_data_sf["geometry"])
plot(Harmonia_adult_research_grade_sf["geometry"])
plot(host_parasite_data_sf["geometry"])
```

```{r}
st_crs(mrc)
head(mrc)
mrc_proj <- st_transform(mrc, crs = 6622)
```

```{r}
st_crs(mrc_qc)
head(mrc_qc)
mrc_qc_proj <- st_transform(mrc_qc, crs = 6622)
```

```{r}
library(ggspatial)
ggplot() +
    geom_sf(data = mrc_qc_proj, inherit.aes = FALSE) +
    geom_sf(data = Harmonia_adult_research_grade_sf, 
            color = "#D55E00", fill = "#D55E00", size = 1, shape = 21, inherit.aes = FALSE) +
    ggtitle("Quebec province") +
    annotation_scale(location = "tr", width_hint = 0.4) +
    annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.3, "in"),
        style = north_arrow_fancy_orienteering) + theme_minimal() -> host_obs

host_obs
```

/FIGURE 4B (upper part)
```{r}
ggsave(filename = "host_obs_FINAL.pdf", plot = host_obs, width = 6, height = 4, dpi = 1000)
```


## Merging new mentions of Hesperomyces harmonia with previous mentions from iNaturalist

```{r}
hesperomyces_obs <- read.csv("Hesperomyces_QC_20250314.csv")
```

```{r}
# Remove the specified columns
hesperomyces_obs_subset <- hesperomyces_obs %>% select(observed_on, url, latitude, longitude, scientific_name, Year, Month)

infected_data_subset <- infected_data %>% select(observed_on, url, latitude, longitude, scientific_name, Year, Month)
#Make the same formats to bind
infected_data_subset <- infected_data_subset %>% 
  mutate_at("observed_on", as.Date) %>% 
  mutate_at(c("url", "scientific_name"), as.character) %>%
  mutate_at(c("Year", "Month"), as.factor)

hesperomyces_obs_subset <- hesperomyces_obs_subset %>% 
  mutate_at("observed_on", as.Date) %>% 
  mutate_at(c("url", "scientific_name"), as.character) %>%
  mutate_at(c("Year", "Month"), as.factor)

# Replace scientific_name values
infected_data_subset <- infected_data_subset %>% mutate(scientific_name = "New_observation_inat")
hesperomyces_obs_subset <- hesperomyces_obs_subset %>% mutate(scientific_name = "Previous_observation_inat")

# Merge the two datasets
hesperomyces_new_obs <- bind_rows(infected_data_subset, hesperomyces_obs_subset)

# Save the merged dataset to your computer
write.csv(hesperomyces_new_obs, "hesperomyces_new_obs_FINAL.csv", row.names = FALSE)
```

```{r}
Harmonia_adult_research_grade_subset <- Harmonia_adult_research_grade %>% select(observed_on, url, latitude, longitude, scientific_name, Year, Month)

host_parasite_data <- bind_rows(hesperomyces_new_obs, Harmonia_adult_research_grade_subset)
```


## correcting four doublons
```{r}
# Function to check for duplicate GPS coordinates and observed_on date
check_duplicates_gps_date <- function(hesperomyces_new_obs) {
  duplicated_entries <- hesperomyces_new_obs[duplicated(hesperomyces_new_obs[, c("latitude", "longitude", "observed_on")]) | duplicated(hesperomyces_new_obs[, c("latitude", "longitude", "observed_on")], fromLast = TRUE), ]
  return(duplicated_entries)
}

# Detect duplicates in Harmonia dataset
duplicates_gps_date <- check_duplicates_gps_date(hesperomyces_new_obs)
print(duplicates_gps_date)
```

```{r}
#28 doublon removed and 3 needs_id removed
urls_to_remove <- c(
  "https://www.inaturalist.org/observations/52381120",
  "https://www.inaturalist.org/observations/84510434",
  "https://www.inaturalist.org/observations/91478224",
  "https://www.inaturalist.org/observations/106546558",
  "https://www.inaturalist.org/observations/95850418",
  "https://www.inaturalist.org/observations/141491024",
  "https://www.inaturalist.org/observations/148600616",
  "https://www.inaturalist.org/observations/128964180",
  "https://www.inaturalist.org/observations/131846281",
  "https://www.inaturalist.org/observations/142460293",
  "https://www.inaturalist.org/observations/172527194",
  "https://www.inaturalist.org/observations/172915232",
  "https://www.inaturalist.org/observations/201363904",
  "https://www.inaturalist.org/observations/180507054",
  "https://www.inaturalist.org/observations/218255836",
  "https://www.inaturalist.org/observations/220711094",
  "https://www.inaturalist.org/observations/229835980",
  "https://www.inaturalist.org/observations/230336267",
  "https://www.inaturalist.org/observations/246211461",
  "https://www.inaturalist.org/observations/239319026",
  "https://www.inaturalist.org/observations/238340007",
  "https://www.inaturalist.org/observations/125106633",
  "https://www.inaturalist.org/observations/137742473",
  "https://www.inaturalist.org/observations/248347563",
  "https://www.inaturalist.org/observations/234749247",
  "https://www.inaturalist.org/observations/188300414",
  "https://www.inaturalist.org/observations/127179625",
  "https://www.inaturalist.org/observations/122942196",
  "https://www.inaturalist.org/observations/216517091", #needs_id, likely pollen but no laboul
  "https://www.inaturalist.org/observations/177254741", #needs_id, likely reflex blood but no laboul
  "https://www.inaturalist.org/observations/223882516" #needs_id
)

# Supposons que ton dataframe s'appelle df
Hesperomyces_new_obs_corrected <- hesperomyces_new_obs %>%
  filter(!url %in% urls_to_remove)

write.csv(Hesperomyces_new_obs_corrected, "hesperomyces_new_obs_corrected_FINAL.csv", row.names = FALSE)

#if done manually
#Hesperomyces_new_obs_corrected <- read.csv("hesperomyces_new_obs_FINAL_corrected_doublon.csv") #load corrected dataset for duplicates; 21 observations removed 
```

```{r}
obs_increase <- Hesperomyces_new_obs_corrected %>%
  count(scientific_name) %>%
  spread(scientific_name, n) %>%
  # Calcul du total actuel
  mutate(Total_current = Previous_observation_inat + New_observation_inat,
         # Calcul de l'augmentation en pourcentage par rapport aux anciennes observations
         obs_increase_percent = ((Total_current - Previous_observation_inat) / Previous_observation_inat) * 100) %>%
  pull(obs_increase_percent)

obs_increase
```

```{r}
hesperomyces_new_obs_counts <- Hesperomyces_new_obs_corrected %>%
  group_by(scientific_name) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
print(hesperomyces_new_obs_counts)
```

```{r}
Hesperomyces_new_obs_corrected$scientific_name <- factor(Hesperomyces_new_obs_corrected$scientific_name, levels = hesperomyces_new_obs_counts$scientific_name)

cb_palette_obs <- c("#CC79A7", "#666666")

Hesperomyces_new_obs_corrected %>% 
  mutate(scientific_name = as.factor(scientific_name)) %>%
  ggplot(aes(x = scientific_name, fill = scientific_name, colour = scientific_name)) + 
  geom_bar(alpha = 0.8) + 
  labs(y = "Number of observations") + 
  guides(colour = FALSE) + 
  mytheme + 
  theme(legend.title = element_text(size = 12), 
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_manual(values = cb_palette_obs) + 
  scale_colour_manual(values = cb_palette_obs) +  theme(aspect.ratio = 0.8) -> obs_plot
```

```{r}
obs_plot
```
/FIGURE 3A
```{r}
ggsave(filename = "obs_plot_FINAL.pdf", plot = obs_plot, width = 4, height = 4, dpi = 1000)
```


## Evolution of Hesperomyces observations through time in Québec
```{r}
hesperomyces_new_obs_cleaned <- Hesperomyces_new_obs_corrected %>% filter(!is.na(observed_on))

Cumulative_data_hesperomyces <- hesperomyces_new_obs_cleaned %>%
  mutate_at("observed_on", as.Date) %>%
  group_by(observed_on, scientific_name) %>%
  summarise(count = n()) %>%
  arrange(observed_on) %>%
  group_by(scientific_name) %>%
  mutate(cum_sum = cumsum(count)) %>%
ungroup() %>%
  complete(observed_on = seq.Date(min(observed_on), max(observed_on), by = "day"), scientific_name, fill = list(count = 0, cum_sum = 0)) %>%
  group_by(scientific_name) %>%
  mutate(cum_sum = cumsum(count))
  
hesperomyces_accumulation_plot <- Cumulative_data_hesperomyces %>%
  ggplot(aes(x = observed_on, y = cum_sum, fill = scientific_name)) + 
  geom_area(alpha = .8) + 
  scale_x_date(limits = as.Date(c("2009-06-05", "2024-10-20"))) + 
  labs(title = "Accumulation curve of Hesperomyces harmoniae in Quebec", 
       x = "Time", 
       y = "Number of observations") + 
  mytheme + 
  scale_fill_manual(values = cb_palette_obs) +  theme(aspect.ratio = 0.8)
```

```{r}
hesperomyces_accumulation_plot
```
/FIGURE 3B
```{r}
ggsave(filename = "hesperomyces_accumulation_plot_FINAL.pdf", plot = hesperomyces_accumulation_plot, width = 6, height = 4, dpi = 1000)
```

```{r}
Hesperomyces_new_obs_corrected$Year <- factor(Hesperomyces_new_obs_corrected$Year, levels = sort(unique(Hesperomyces_new_obs_corrected$Year)))

Hesperomyces_new_obs_corrected$Month <- factor(Hesperomyces_new_obs_corrected$Month, levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

library(RColorBrewer)
cb_palette_year <- brewer.pal(12, "Set2")

Hesperomyces_new_obs_corrected %>% 
  filter(!is.na(observed_on)) %>%
  mutate(Month = as.factor(Month)) %>%
  ggplot(aes(x = Month, fill = scientific_name)) + 
  geom_bar(alpha = 0.8) + 
  mytheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = cb_palette_obs) +  theme(aspect.ratio = 0.8) -> hesperomyces_month_plot

Hesperomyces_new_obs_corrected %>% 
  filter(!is.na(observed_on)) %>%
  mutate(Year = as.factor(Year)) %>%
  ggplot(aes(x = Year, fill = scientific_name)) + 
  geom_bar(alpha = 0.8) + 
  mytheme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = cb_palette_obs) +  theme(aspect.ratio = 0.8) -> hesperomyces_year_plot
```

```{r}
hesperomyces_year_plot
```

/Figure 3C
```{r}
ggsave(filename = "hesperomyces_year_plot_FINAL.pdf", plot = hesperomyces_year_plot, width = 6, height = 4, dpi = 1000)
```

```{r}
hesperomyces_month_plot
```

/Figure 3D
```{r}
ggsave(filename = "hesperomyces_month_plot_FINAL.pdf", plot = hesperomyces_month_plot, width = 6, height = 4, dpi = 1000)
```

##Geospatial analysis of Hesperomyces observations across Québec
```{r}
hesperomyces_new_obs_corrected_sf <- st_as_sf(Hesperomyces_new_obs_corrected, coords = c("longitude", "latitude"), crs = 4326)

plot(hesperomyces_new_obs_corrected_sf["geometry"])
```

```{r}
theme_set(theme_test())
ggplot() +
  geom_sf(data = mrc_qc_proj) +
  geom_sf(
    data = hesperomyces_new_obs_corrected_sf,
    aes(fill = scientific_name, color = scientific_name),
    shape = 21, size = 1
  ) +
  scale_fill_manual(values = cb_palette_obs) +
  scale_color_manual(guide = FALSE, values = cb_palette_obs) +
  ggtitle("Quebec province") +
    annotation_scale(location = "tr", width_hint = 0.4) +
    annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.3, "in"),
        style = north_arrow_fancy_orienteering) +
  theme_minimal() -> map_hesperomyces
map_hesperomyces
```
/Figure 4A (upper part)
```{r}
ggsave(filename = "map_hesperomyces_FINAL.pdf", plot = map_hesperomyces, width = 6, height = 4, dpi = 1000)
```

```{r}
ggplot(data = hesperomyces_new_obs_corrected_sf) +
    geom_sf() +
    coord_sf(crs = 6622)
```


## Map zooming
```{r}
theme_set(theme_test()) 

ggplot(data = hesperomyces_new_obs_corrected_sf) + 
  geom_sf(data = mrc_qc_proj) + 
  geom_sf(aes(fill = scientific_name, color = scientific_name), size = 2) + 
  scale_fill_manual(values = cb_palette_obs) +
  scale_color_manual(guide = FALSE, values = cb_palette_obs) +
  coord_sf(xlim = c(-80, -62), ylim = c(45, 51)) -> map_hesperomyces_zoom 

ggplot(data = Harmonia_adult_research_grade_sf) + 
  geom_sf(data = mrc_qc_proj) + 
  geom_sf(aes(fill = Age, color = Age), size = 2) + 
  scale_fill_manual(values = "#D55E00") +
  scale_color_manual(guide = FALSE, values = "#D55E00") +
  coord_sf(xlim = c(-80, -62), ylim = c(45, 51)) -> map_host_zoom
```

```{r}
map_hesperomyces_zoom
```
/Figure 4A (bottom part)
```{r}
ggsave(filename = "map_hesperomyces_zoom_FINAL.pdf", plot = map_hesperomyces_zoom, width = 6, height = 4, dpi = 1000)
```

```{r}
map_host_zoom
```
/Figure 4B (bottom part)
```{r}
ggsave(filename = "map_host_zoom_FINAL.pdf", plot = map_host_zoom, width = 6, height = 4, dpi = 1000)
```


Last updated 23 August 2025 by Jonathan Cazabonne


